manuscript_analysis

### 2024-07-03 manuscript_analysis.Rmd
stats function has been run

#df1 and df2 are the fastest ones
# predictions() can also be used directly with df_models -> takes longer
# BECAUSE OF TYPO: RE RUN TEMP + DEPTH models from df1-3, df4 still needs to be run & stats overview too

@@

# statistics of the gamms
total_models <- bind_rows(df_1, df_2, df_3, df_4)

@@

  model_0 <- gam(data = data, Abundance ~ s(mean_last_7days, k = 3) +
                   s(Depth_sample, k = 3)
                            + s(fLake, bs = 're')
                            +  s(fProtocol, bs = 're'), family = ziP())
  print(glance(model_0))
# new models

@@

@@

# trying to group by category and color
predictions_categories |>
  ggplot(aes(temp, fit)) +
  geom_ribbon(aes(ymin = (fit - se.fit), ymax = (fit + se.fit), fill = factor(category)), alpha = 0.3) +
  geom_line(aes(color = factor(category))) +
  theme_bw() +
  facet_wrap(~species + category, scale = "free_y", labeller = labeller(species = label_wrap_gen(width = 10))) +
  theme(strip.background = element_rect(fill = "lightgrey"), strip.text = element_text(size = 6)) +
  scale_color_manual(values = mycolors1, aesthetics = c("color", "fill")) +
  xlab("Temperature") +
  ylab("Abundance")

>>>>

@@

# issue with cottus sp po
# statistics of the gamms
total_models <- bind_rows(df_1, df_2, df_3, df_4)

@@

  model_0 <- gam(data = data, Abundance ~ s(mean_last_7days, k = 3) +
                   s(Depth_sample, k = 3)
                            + s(fLake, bs = 're')
                            +  s(fProtocol, bs = 're'), family = ziP())
  print(glance(model_0))

@@

# AIC_testing(df_4, "Cottus_sp_Po")
# # best model is the temp, depth model

@@

# trying to group by category and color
figure_test_2 <- predictions_categories |>
  ggplot(aes(temp, fit)) +
  geom_ribbon(aes(ymin = (fit - se.fit), ymax = (fit + se.fit), fill = factor(category)), alpha = 0.3) +
  geom_line(aes(color = factor(category))) +
  theme_bw() +
  facet_wrap(~species + category, scale = "free_y", labeller = labeller(species = label_wrap_gen(width = 10))) +
  theme(strip.background = element_rect(fill = "lightgrey"), strip.text = element_text(size = 6)) +
  scale_color_manual(values = mycolors1, aesthetics = c("color", "fill")) +
  xlab("Temperature") +
  ylab("Abundance")

# tiff(paste("total_models/plots/draft_all_predictions.tiff", sep = ""), units="in", width = 12, height=8, res=300)
# plot(figure_test_2)
# 
# # Closing the graphical device
# dev.off()
